Carbonate chemistry at Ny-Ålesund

### 2021-11-25 awipev-CO2.Rmd
work on seafet profile

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))

# remove outliers
quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))

>>>>

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, montht) %>% 
  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
                mean = mean(pHint_tot_sf, na.rm =TRUE),
                sd = sd(pHint_tot_sf, na.rm =TRUE)
                ) %>% 
  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
